Higher-Order unification for free!

### 2024-05-03 paper/main.tex
reformulate definition progress-eta-rhs

\newcommand{\progressetaright}{\emph{$\eta$-progress-\rhs}\xspace}
\begin{definition}[\progressetaright]\label{def:progressetaright} A link
\linketaM{\Gamma}{X}{T} is removed from \linkStore when either 1)
$\testmaybeeta~T$ does not hold (anymore) or 2) by $\eta$-contracting $T$ to
$T'$ where $T'$ does not start with the \elpiIn{lam} constructor. In the
first case, $X$ is unified with $T$, and in the second one, $X$ is unified with
$T'$ (under the context $\Gamma$).
\end{definition}
\todo{reformulate, maybe with itemize, too messy}

The idea behind this rule is to instantiate the variable of a \linketa
whenever its \rhs is for sure a \wellb term.

>>>>

\newcommand{\progressetaright}{\emph{$\eta$-progress-\rhs}\xspace}
\begin{definition}[\progressetaright]\label{def:progressetaright} A link
\linketaM{\Gamma}{X}{T} is removed from \linkStore when either 
\begin{itemize}
  \item $\testmaybeeta~T$ does not hold (anymore). In this case $X$ is unified
        with $T$
  \item $T$ $\eta$-contracts to a term $T'$ not starting with the \elpiIn{lam}
        constructor. In this case $X$ is unified with $T'$
\end{itemize}
\end{definition}

The idea behind this rule is to instantiate the \lhs variable of a \linketa
whenever its \rhs is for sure a \wellb term.
